\section{Summary}
\label{sec:summary}

We have discussed two of the three aspects one needs to take into account
to simulate the ICD spectrum of rare gas clusters properly. Due to the nature
of clusters, a neon atom ionized in the inner-valence will have several decay
partners at different distances. The larger the interatomic distance is the higher
is the kinetic energy of the ICD electrons which will yield a multitude of
peaks in the spectrum. These are then weighted by the decay width, which
depends on the interatomic distance of the decay partners but also needs
to be scaled by the number of pairs of the same distance.
The manifold of all different decay events will then yield the spectrum.

When applying these aspects to cluster structures, one finds that not only
the nearest neighbours contribute to the spectrum, but several other decay
partners do as well. Decay partners until a distance of at least twice the
distance of the clostest decay partners should be taken into account.
In clusters with an icosahedral cluster structure this is especially important
because the smallest interatomic distance between atoms of the same and atoms
of different layers is different, but both distances are comparable.
This leads to a different number of peaks in the spectra which might help to
distinguish between clusters of icosahedral and cuboctahedral cluster structure.

While the theoretical lifetime of the bulk atoms show an excellent agreement
with experiment, the lifetimes of the surface atoms differ significantly.
This deviation
might be caused by different static cluster structures than taken into account
in this work, by different energetic stabilization of charges or by nuclear
dynamics. Which of these reasons explains the experiment can not be determined
at the moment. Experimentally determined photoelectron spectra of the outer
valence of high resolution in neon clusters would help to solve this puzzle.
